Towards typed repositories of proofs

### 2010-06-18 papers/MIPS2010/abstract.tex
* Tentative de reformulation de l approche a base de theorie des types
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@118 403e655e-980a-47bd-8c60-1ee5348bb6b7

We propose to discuss a small part of these questions, namely the
enhancement and adaptation of version control paradigms to the
management of mathematical repositories, to witness with more
precision the \emph{impact of changes}. In proof assistants based on
the propositions-as-types paradigm, Type Theory offers a powerful tool
to witness the effect of changes finely: types, and we base our work
on these.

We will describe some of the possible directions to develop a tool to
analyze the impact of change through types. It involves at its core a
typed description language for repositories, and is strongly related
to incremental type-checking: only differences between versions are
type-checked and not the entire development. In the first iteration of
this project, we focus on a static, or data-driven model for
repositories inspired by the repository model of \textsf{GIT}.

>>>>

We propose to discuss a small part of these questions, namely the
enhancement and adaptation of version control paradigms to the
management of mathematical repositories, to witness with more
precision the \emph{impact of changes}. Following the Type Theory
approach, our work is based on an algebra of expressive types that are
meant to assign precise specifications to object-level term
constructors and, in the meantime, to capture fine-grained
dependencies between these objects.

%% In proof assistants based on
%% the propositions-as-types paradigm, Type Theory offers a powerful tool
%% to witness the effect of changes finely: types, and we base our work
%% on these.

We will describe some of the possible directions to develop a tool to
analyze the impact of changes through types. It involves at its core a
typed description language for repositories, and is strongly related
to incremental type-checking: only differences between versions are
type-checked and not the entire development. In the first iteration of
this project, we focus on a static, or data-driven model for
repositories inspired by the repository model of \textsf{GIT}.
